### 2019-05-15 dantzig_selector/report/4_simulation.tex
Correct vectorize convention
Draft: Matrices generation
Reorganize source files
Proof: Concentration ineq. of

As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\Mc {R} \SB {h}}.
But it is not the end.
In fact, Cand\`es and Tao's analysis in ``\m {\ell_1}-MAGIC'' transforms DS into a linear program (LP), but that does not directly applies
Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
Thus our proposed algorithm is not a corollary of the DS program outlines in ``\m {\ell_1}-MAGIC''.

@@

\Result
{Definition}
{
For \m {\V{x} \in \Mb {V}_{\Mb {C}} \SB {M}}, we say that \m {\Mc {R} \SB {\V{x}}} is the real representation of \m {\V{x}}, defined by
%
\Disp {
\NC \Mc {R} \SB {\V{x}}
\in \NC \Mb {V}_{\Mb {R}} \SB {2M} \NR
\NC \Mc {R} \SB {\V{x}} \DB {m} =
\NC \startcases
\NC \Mf {Re} \SB {\V{x} \DB {m'}}, \MC m =2m' \NR
\NC \Mf {Im} \SB {\V{x} \DB {m'}}, \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' 
= \NC  0, 1, 2, \dots, M-1 \NR
}
The bijectivity is obvious, and we define \m {\Mc {R} ^{-1}} so that
\Disp {
\NC \Mc {R} ^{-1} \SB {\Mc {R} \SB {\V{x}}}
=\NC \V{x} \NR[+]
}
}

@@

\Result
{Definition}
{
For \m {\M{A} \in \Mb {M}_{\Mb {C}} \SB {M_1, M_2}}, we say that \m {\Mc {R} \SB {\M{A}}} is the real representation of \m {\M{A}}, defined by
%
\Disp {
\NC \Mc {R} \SB {\M{A}}
\in \NC \Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2} \NR
\NC \Mc {R} \SB {\M{A}} \DB {m_1,m_2} =
\NC \startcases
\NC \Mf {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
\NC \Mf {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
\NC -\Mf {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
\NC \Mf {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\stopcases \NR[+]
\NC m_1 
= \NC 0, 1, 2, \dots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \dots, M_2 -1 \NR
}
Notice that Here not all matrices in \m {\Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2}} are images, and we will not call the inverse function anyway.
}

@@

\Disp {
\NC \T {\V {y}}
\in \NC \Mb {V}_{\Mb {R}} \SB {2N_y} \NR
\NC \T {\V {y}}
= \NC \Mc {R} \SB {\V {y}} \NR[+]
\NC \T {\V {g}}
\in \NC \Mb {V}_{\Mb {R}} \SB {2N_h} \NR
\NC \T {\V {g}}
= \NC \Mc {R} \SB {\V {g}} \NR[+]
\NC \T {\M {P}}
\in \NC \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_h} \NR
\NC \T {\M {P}}
= \NC \Mc {R} \SB {\M {P}} \NR[+]
\NC \T {\V {z}}
\in \NC \Mb {V}_{\Mb {R}} \SB {2N_y} \NR
\NC \T {\V {z}}
= \NC \Mc {R} \SB {\V {z}} \NR[+]
}
%
such that, by construction,
%
\Disp {
\NC \V {\T {y}}
= \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}}
}
%

@@

%
\Disp {
\NC {\V {u}}_{n_h}
\in \NC \Mb {V}_{\Mb {R}} \SB {N_h} \NR
\NC {\V {u}}_{n_h} \DB {n_h'}
= \NC
\startcases
1, \quad \MC n_h' =n_h \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC {\T {\M {U}}}_{n_h} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR
\NC {\T {\M {U}}}_{n_h} \DB {n_h', n_h''}
= \NC
\startcases
1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h \NR
1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h \NR
1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h +1 \NR
1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC n_h, n_h', n_h'' 
= \NC 0, 1, 2, \dots, N_h -1 \NR
}
Moreover, denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
Now, if we introduce vector \m{\V{m}}

\Disp{
\NC \V {m} \NC \in \Mb {V}_{\Mb {R}} \SB {N_h} \NR
\NC \V{m} \DB{n_h}
= \NC \Nm{\V{g} \DB{n_h}} \NR[+]
\NC n_h, n_h', n_h'' 
= \NC 0, 1, 2, \dots, N_h -1 \NR
}

to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now take the form
\Disp {
\NC \Hat {\T {\V {g}}}
= \NC \startcases
\NC \Min {\T {\V {g}}', \V {m}} \quad
\MC \IP { \V {1}, \V {m} } \NR
\NC \Mr {subject} \; \Mr {to} \quad
\MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
\leq \IP { \V {u}_{n_h}, \V {m} } \NR
\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
\leq \g \NR
\stopcases \NR[+]
\NC n_h 
= \NC 0, 1, 2, \dots, N_h-1 \NR
}

@@

\Disp{
\NC \V{t}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {3N_h} \NR
\NC \V{x}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {3N_h} \NR
\NC \M{A}_i
\NC \in \Mb {M}_{\Mb {R}} \SB {2N_h, 3N_h} \NR
\NC \V{b}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {3N_h} \NR
\NC \V{c}_i
\NC \in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR
\NC d_i
\NC \in \Mb {R} \NR
}

@@

\Disp{
\NC \V{t}
= \NC \startthematrix
\NC \V{0} \NR
\NC \V{1} \NR
\stopthematrix \NR[+]
\NC \V{x}'
= \NC \startthematrix
\NC \T {\V {g}}' \NR
\NC \V{m} \NR
\stopthematrix \NR[+]
}

@@

\Disp{
\NC \M{A}_i
= \NC \startthematrix
\NC \T {\M {U}}_{i}, \NC \M{0} \NR
\stopthematrix \NR[+]
\NC \V{b}_i
= \NC \V{0} \NR[+]
\NC \V{c}_i
= \NC \startthematrix
\NC \V{0} \NR
\NC \V {u}_{i} \NR
\stopthematrix \NR[+]
\NC d_i
= \NC 0 \NR[+]
\NC i 
= \NC 0, 1, 2, \dots, N_h -1 \NR
}

@@

\Disp{
\NC \M{A}_i
= \NC \startthematrix
\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
\stopthematrix \NR[+]
\NC \V{b}_i
=\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}} \NR[+]
\NC \V{c}_i
= \NC \startthematrix
\NC \V{0} \NR
\NC \V{0} \NR
\stopthematrix \NR[+]
\NC d_i
= \NC \g \NR[+]
\NC i 
= \NC N_h, N_h +1, N_h +2, \dots, 2N_h -1 \NR
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_y}}, \m{\g \geq 0}.
\item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
\item Calculate
\Disp{
\NC \Hat {\V {x}}
= \NC \startcases
\NC \Min {\V {x}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}
\MC \IP {\V {t}, \V {x}'} \NR[+]
\NC \Mr {subject} \; \Mr {to}
\quad  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
\leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
\NC \MC i =0, 1, 2, \dots, 2N_h -1 \NR
\stopcases \NR[+]
}
\item Extract
\Disp{
\NC \Hat{\T{\V{g}}} =\NC \Hat{\V{x}} \DB {0 : 2N_h-1} \NR[+]
}
\item Convert 
\Disp{
\NC \Hat{\V{g}} =\NC \Mc{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {G} =\NC \Mr {vec}^{-1} \SB {\Hat {g}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {\M {H}} =\NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

>>>>

As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} \SB {h}}.
But it is not the end.
In fact, Cand\`es and Tao's analysis in ``\m {\ell_1}-MAGIC'' transforms DS into a linear program (LP), but that does not directly applies
Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
Thus our proposed algorithm is not a corollary of the DS program outlines in ``\m {\ell_1}-MAGIC''.

@@

\Result
{Definition}
{
For \m {\V{x} \in \MB {V}_{\MB {C}} \SB {M}}, we say that \m {\MC {R} \SB {\V{x}}} is the real representation of \m {\V{x}}, defined by
\Disp {
\NC \MC {R} \SB {\V{x}}
\in \NC \MB {V}_{\MB {R}} \SB {2M} \NR
\NC \MC {R} \SB {\V{x}} \DB {m}
= \NC \startcases
\NC \MF {Re} \SB {\V{x} \DB {m'}}, \MC m =2m' \NR
\NC \MF {Im} \SB {\V{x} \DB {m'}}, \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' 
= \NC  0, 1, 2, \dots, M-1 \NR
}
The bijectivity is obvious, and we define \m {\MC {R} ^{-1}} so that
\Disp {
\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V{x}}}
=\NC \V{x} \NR[+]
}
}

@@

\Result
{Definition}
{
For \m {\M{A} \in \MB {M}_{\MB {C}} \SB {M_1, M_2}}, we say that \m {\MC {R} \SB {\M{A}}} is the real representation of \m {\M{A}}, defined by
\Disp {
\NC \MC {R} \SB {\M{A}}
\in \NC \MB {M}_{\MB {R}} \SB {2M_1, 2M_2} \NR
\NC \MC {R} \SB {\M{A}} \DB {m_1,m_2} =
\NC \startcases
\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
\NC \MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
\NC -\MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\stopcases \NR[+]
\NC m_1 
= \NC 0, 1, 2, \dots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \dots, M_2 -1 \NR
}
Notice that Here not all matrices in \m {\MB {M}_{\MB {R}} \SB {2M_1, 2M_2}} are images, and we will not call the inverse function anyway.
}

@@

\Disp {
\NC \T {\V {y}}
\in \NC \MB {V}_{\MB {R}} \SB {2N_y} \NR
\NC \T {\V {y}}
= \NC \MC {R} \SB {\V {y}} \NR[+]
\NC \T {\V {g}}
\in \NC \MB {V}_{\MB {R}} \SB {2N_h} \NR
\NC \T {\V {g}}
= \NC \MC {R} \SB {\V {g}} \NR[+]
\NC \T {\M {P}}
\in \NC \MB {M}_{\MB {R}} \SB {2N_y, 2N_h} \NR
\NC \T {\M {P}}
= \NC \MC {R} \SB {\M {P}} \NR[+]
\NC \T {\M {P}} ^\Adj
\in \NC \MB {M}_{\MB {R}} \SB {2N_y, 2N_h} \NR
\NC \T {\M {P}} ^\Adj
= \NC \MC {R} \SB {\M {P} ^\Adj} \NR[+]
\NC \T {\V {z}}
\in \NC \MB {V}_{\MB {R}} \SB {2N_y} \NR
\NC \T {\V {z}}
= \NC \MC {R} \SB {\V {z}} \NR[+]
}
such that, by construction,
\Disp {
\NC \V {\T {y}}
= \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}}
}

@@

\Disp {
\NC {\V {u}}_{n_h}
\in \NC \MB {V}_{\MB {R}} \SB {N_h} \NR
\NC {\V {u}}_{n_h} \DB {n_h'}
= \NC
\startcases
1, \quad \MC n_h' =n_h \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC {\T {\M {U}}}_{n_h} \in \NC \MB {M}_{\MB {R}} \SB {2N_h, 2N_h} \NR
\NC {\T {\M {U}}}_{n_h} \DB {n_h', n_h''}
= \NC
\startcases
1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h \NR
1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC n_h, n_h', n_h'' 
= \NC 0, 1, 2, \dots, N_h -1 \NR
}
Moreover, denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
Now, if we introduce vector \m{\V{m}}

\Disp{
\NC \V {m} \NC \in \MB {V}_{\MB {R}} \SB {N_h} \NR
\NC \V{m} \DB{n_h}
= \NC \Nm{\V{g} \DB{n_h}} \NR[+]
\NC n_h, n_h', n_h'' 
= \NC 0, 1, 2, \dots, N_h -1 \NR
}

to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now take the form
\Disp {
\NC \Hat {\T {\V {g}}}
= \NC \startcases
\NC \Min {\T {\V {g}}', \V {m}} \quad
\MC \IP { \V {1}, \V {m} } \NR
\NC \Rm {subject} \; \Rm {to} \quad
\MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
\leq \IP { \V {u}_{n_h}, \V {m} } \NR
\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
\leq \g \NR
\stopcases \NR[+]
\NC n_h 
= \NC 0, 1, 2, \dots, N_h-1 \NR
}

@@

\Disp{
\NC \V{t}_i
\NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
\NC \V{x}_i
\NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
\NC \M{A}_i
\NC \in \MB {M}_{\MB {R}} \SB {2N_h, 3N_h} \NR
\NC \V{b}_i
\NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
\NC \V{c}_i
\NC \in \MB {V}_{\MB {R}} \SB {2N_h} \NR
\NC d_i
\NC \in \MB {R} ^+ \NR
}

@@

\Disp{
\NC \V{t}
= \NC \startTheMatrix
\NC \V{0} \NR
\NC \V{1} \NR
\stopTheMatrix \NR[+]
\NC \V{x}'
= \NC \startTheMatrix
\NC \T {\V {g}}' \NR
\NC \V{m} \NR
\stopTheMatrix \NR[+]
}

@@

\Disp{
\NC \M{A}_i
= \NC \startTheMatrix
\NC \T {\M {U}}_{i}, \NC \M{0} \NR
\stopTheMatrix \NR[+]
\NC \V{b}_i
= \NC \V{0} \NR[+]
\NC \V{c}_i
= \NC \startTheMatrix
\NC \V{0} \NR
\NC \V {u}_{i} \NR
\stopTheMatrix \NR[+]
\NC d_i
= \NC 0 \NR[+]
\NC i 
= \NC 0, 1, 2, \dots, N_h -1 \NR
}

@@

\Disp{
\NC \M{A}_i
= \NC \startTheMatrix
\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
\stopTheMatrix \NR[+]
\NC \V{b}_i
=\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}} \NR[+]
\NC \V{c}_i
= \NC \V{0} \NR[+]
\NC d_i
= \NC \g \NR[+]
\NC i 
= \NC N_h, N_h +1, N_h +2, \dots, 2N_h -1 \NR
}

@@

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_y}}, \m{\g > 0}.
\item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
\item Calculate
\Disp{
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}' \in \MB {V}_{\MB {C}} \SB {N_h}}
\MC \IP {\V {t}, \V {x}'} \NR[+]
\NC \Rm {subject} \; \Rm {to}
\quad  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
\leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
\NC \MC i 
=0, 1, 2, \dots, 2N_h -1 \NR
\stopcases \NR[+]
}
\item Extract
\Disp{
\NC \Hat{\T{\V{g}}}
\LA \NC \Hat{\V{x}} \DB {0 : 2N_h-1} \NR[+]
}
\item Convert 
\Disp{
\NC \Hat{\V{g}}
\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR[+]
}
\item Calculate
\Disp {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}
